\Title

### 2021-01-27 manuscript/manuscript.tex
Review the conclusions section
Trimmed it a little bit and added a final part on future research.

The equivalent source technique has been proven to be a well suited method for
interpolating any harmonic data such as gravity disturbances and magnetic
anomalies.
The two main reasons that make it to stand out over all-purpose 2D
interpolation methods is the fact that the equivalent sources take into account
the height of the observations and they always produce harmonic predictions.
The main inconvenience of using equivalent sources is the computational
requirements needed to estimate the coefficients of the equivalent sources,
specially on the computer memory needed to store the Jacobian matrix.
This forbids the application of the equivalent source technique to very
large datasets where the computer memory needed to store the whole Jacobian
matrix greatly exceeds the specifications of modest personal computers now days.

In this work we present two strategies that could be simultaneously applied in
order to interpolate very large datasets in reasonable times without the need
to store large matrices into memory:
the block-averaged sources, which reduce the number of
equivalent sources needed for the interpolation;
and the gradient-boosted equivalent sources that simplify the
problem of estimating the source coefficients into smaller problems
through sets of equivalent sources defined by overlapping windows.

Both methods were exhaustively tested against a synthetic model and synthetic
surveys in order to compare accurate they are in comparison to the existing
techniques and how they perform in terms of computational resources.
Block-averaged sources were compared to the interpolations obtained with two
traditional strategies for locating the sources:
the \emph{source below data} and the \emph{regular grid} of sources.
The performance of the gradient-boosted equivalent sources was compared against
the regular non-boosted equivalent sources, along with tests for assessing how
the choice of the window size and the amount of overlap between adjacent
windows affect both the accuracy of the interpolations and the computational
load.

Our results showed that the block-averaged sources reduce the computational
load needed to estimate their coefficients in comparison to the two traditional
strategies mentioned before.
They also showed that this reduction of the number of sources doesn't affect
the accuracy of the predictions, making block-averaged sources a better
alternative to the traditional methods.
Besides, block-averaged sources might also prevent aliasing on the interpolated
values, specially when the observation points show high anisotropy, i.e. they
were taken along paths with a high sample frequency.
From our experimentation with this new strategy we noticed that special
attention must be payed when choosing the size of the block spacing:
as a thumb rule, it must be approximately equal to the resolution of the
regular grid where the values will be interpolated.

We have also carried out similar tests to compare the vertical location of the
sources.
Our results showed that any one of the three strategies taken into account
(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
doesn't significantly affects the accuracy of the interpolations.
Nevertheless, we are more prone to choose either the \emph{constant depth} or
the \emph{relative depth} for any application because they involve less
hyper-parameters that would be needed to estimated before the actual
interpolation.

Regarding the gradient-boosted equivalent sources, our results show that they
heavily reduce the computer memory needed to estimate source coefficients,
making possible to interpolate even very large datasets.
The interpolations obtained though this new method achieve almost the same
accuracy than the non-boosted sources, while reducing the computation time
needed to estimate the source coefficients.
Because it doesn't involve any assumption on the location of the sources, it
can be used in conjunction with any horizontal source layout and any strategy
for setting their depth.
This allows to use both the block-averaged sources and the gradient-boosted
equivalent sources simultaneously.
Our results allowed us to develop a rule of thumb in order to maximize the
accuracy of the interpolations: the size of the overlapping windows must be
chosen as the maximum value that creates Jacobian matrices that fit into our
computer memory.
Therefore its choice is subject to the particular infrastructure where the
interpolation will be carried out.
We also show that an overlap of 50\% between adjacent windows achieves a good
compromise between accuracy and computation time needed to fit the source
coefficients.

Finally, both proposed methods were used to interpolate a compilation of more
than 1.7 million gravity points from Australia on a regular grid with
a resolution of 1~arc-minute.
The whole process was carried out on a modest personal computer, requiring
a maximum of 10GB of memory.
This shows how the new gradient-boosted equivalent sources can be applied to
real-world data.

>>>>

The equivalent source technique has been proven to be well suited for
interpolating gravity disturbances and magnetic anomalies.
The two main reasons that make it to stand out from other 2D interpolation
methods is the fact that the equivalent sources take into account the height of
the observations and that the interpolated values will always be harmonic
functions.
The main challenge to using equivalent sources in practice is the high
computational load of estimating the coefficients of the equivalent sources,
specially on the computer memory needed to store the Jacobian matrix.
In this work we present two strategies that could be simultaneously applied in
order to interpolate very large datasets (millions of points) in reasonable
computation times on modest hardware:
block-averaging source locations, which reduce the number of equivalent sources
needed for the interpolation,
and the gradient-boosted equivalent source algorithm, which breaks down the
inverse problem into smaller  sets of equivalent sources defined by overlapping
windows.
Both methods were tested against synthetic datasets in order to compare their
accuracy and how they perform in terms of computational resources.

Our results show that the block-averaged sources reduce the computational
load needed to estimate source coefficients in comparison to the two traditional
strategies of placing sources below data points or on regular grids.
We also showed that this reduction of the number of sources does not affect
the accuracy of the predictions.
The use of block-averaged sources may also prevent aliasing of the interpolated
values, specially when the observations are unevenly sampled (e.g., airborne
and shipborne surveys).
Special attention must be payed when choosing the size of the blocks for
averaging: as a thumb rule, we recommend choosing a size approximately equal to
the resolution of the regular grid where the values will be interpolated.

Tests that compared strategies for the vertical location of the
sources showed that any one of the three strategies tested
(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
produces comparable accuracy of interpolation.
Nevertheless, we are more prone to recommending either the \emph{constant
depth} or the \emph{relative depth} for most applications because they involve
less hyper-parameters that would be needed to configured before the actual
interpolation.

Gradient-boosted equivalent sources were shown to heavily reduce the computer
memory needed to estimate source coefficients, making it possible to
interpolate large datasets with millions of points that would otherwise produce
Jacobian matrices larger than the available memory.
The interpolations obtained though this new method achieve close to the same
accuracy than the regular equivalent sources (within approximately 40\%), while
reducing the computation time needed to estimate the source coefficients by
approximately three times.
We also show that an overlap of 50\% between adjacent windows achieves a good
compromise between accuracy and computation time.
The size of the overlapping windows should be chosen as the maximum value
possible that creates Jacobian matrices that still fit into computer memory.

The gradient-boosting method developed here can be used in conjunction with any
horizontal source layout, depth strategy, or source type (e.g., point sources,
prisms, tesseroids) because it does not rely on assumptions about the sources.
Future research should investigate the application of gradient boosting to
other equivalent source methods, as well as alternatives to overlapping windows
for converting the equivalent source model into an additive model.
